\documentclass[a4paper,12pt]{exam}
%\usepackage{times}
\usepackage{multicol}
\usepackage{soul,supertabular,shortlst}
\usepackage[modulo]{lineno}
\usepackage{mathrsfs,pifont}
\usepackage{stmaryrd}
\usepackage{amsmath}
\usepackage[cdot,thinqspace]{SIunits}
\usepackage[a4paper]{geometry}
\usepackage{lastpage}
\Fullpages
\NumberOfVersions{1}
\usepackage{CJK}
\ifx\pdfoutput\undefined
\usepackage[dvipdfm]{graphicx}
\else
\usepackage[pdftex]{graphicx}
\fi
\usepackage[usenames,dvipsnames]{color}
\usepackage{indentfirst}
\usepackage{float}
%\usepackage{floatflt}
\newcommand{\chuhao}{\fontsize{42pt}{\baselineskip}\selectfont}
\newcommand{\xiaochuhao}{\fontsize{36pt}{\baselineskip}\selectfont}
\newcommand{\yihao}{\fontsize{28pt}{\baselineskip}\selectfont}
\newcommand{\erhao}{\fontsize{21pt}{\baselineskip}\selectfont}
\newcommand{\xiaoerhao}{\fontsize{18pt}{\baselineskip}\selectfont}
\newcommand{\sanhao}{\fontsize{15.75pt}{\baselineskip}\selectfont}
\newcommand{\sihao}{\fontsize{14pt}{\baselineskip}\selectfont}
\newcommand{\xiaosihao}{\fontsize{12pt}{\baselineskip}\selectfont}
\newcommand{\wuhao}{\fontsize{10.5pt}{\baselineskip}\selectfont}
\newcommand{\xiaowuhao}{\fontsize{9pt}{\baselineskip}\selectfont}
\newcommand{\liuhao}{\fontsize{7.875pt}{\baselineskip}\selectfont}
\newcommand{\qihao}{\fontsize{5.25pt}{\baselineskip}\selectfont}

\def\Varangle#1{\kern.75pt\vtop{\hbox{\kern-.75pt$/{#1}$}\kern-.35pt\hrule}}

\begin{document}
\begin{CJK*}{GBK}{song}
\CJKtilde
%\CJKcaption{GB}
\DeclareGraphicsExtensions{.pdf}
%\renewcommand\figurename{图}
\renewcommand\linenumberfont{\normalfont\scriptsize\sffamily}
\nolinenumbers
\newcommand\AnswerLeading{Answer}
\SectionPrefix{Section \Roman{sectionindex}. \space}
% \NoKey
\NoRearrange
\ConstantBlanks{3cm}
\ContinuousNumbering
\ShortKey
\SectionFont{\large\bf}
\examname{专业英语}
\DefineAnswerWrapper{\begin{description}\item [\AnswerLeading:]}{\end{description}}
\def\namedata{学号：\underline{\hspace{51pt}}\hspace{17pt}姓名：\underline{\hspace{51pt}}\hspace{17pt}成绩：\underline{\hspace{51pt}}}
\class{院系：\underline{\hspace{51pt}}\hspace{17pt}年级：\underline{\hspace{51pt}}\hspace{17pt}专业：\underline{\hspace{51pt}}}
\begin{examtop}
\setcounter{version}{2}
\begin{center}
\begin{tabular}{r}
{\Large \bf苏州大学\underline{\examtype}课程试卷
}\hspace{17pt}(\textsf{\Alph{version}})~卷\hspace{17pt}共~8~页\medskip\\考试形式\underline{闭}卷\hspace{17pt}2003~年~11~月
\end{tabular}
\\\bigskip
\classdata\\ \namedata
\end{center}
\bigskip
\end{examtop}
\begin{keytop}
\begin{center}
{\bf\Large 苏州大学\underline{\examtype}课程}\hspace{17pt}(\textsf{\Alph{version}})~卷参考答案\hspace{17pt}共~\pageref{LastPage}~页\bigskip\\
院系：\underline{\hspace{51pt}}\hspace{17pt}专业：\underline{\hspace{51pt}}
\end{center}
\bigskip
\end{keytop}

\begin{fillin}[title={Word Translation.(15 pts.)}, examcolumns=2, keycolumns=2]
\noindent{\bf Directions: }{\em Translate the following words into Chinese if it's in English, and
into English if in Chinese. If the word is an initial or abbreviation,
its full form is needed.}
    \begin{question}
	encrypt \blank{加密}
    \end{question}
    \begin{question}
	inductance \blank{电感量}
    \end{question}
    \begin{question}
	analog \blank{模拟的}
    \end{question}
    \begin{question}
	multiplex \blank{多路复用}
    \end{question}
    \begin{question}
	Superposition Theorem \blank{叠加定律}
    \end{question}
    \begin{question}
	TTL \blank{Transistor-Transistor Logic}
    \end{question}
    \begin{question}
	channel \blank{信道}
    \end{question}
    \begin{question}
	impedance \blank{阻抗}
    \end{question}
    \begin{question}
	负载 \blank{load}
    \end{question}
    \begin{question}
	天线 \blank{antenna}
    \end{question}
    \begin{question}
	地 \blank{ground}
    \end{question}
    \begin{question}
	解调 \blank{demodulation}
    \end{question}
    \begin{question}
	纯文本 \blank{plain text}
    \end{question}
    \begin{question}
	光学字符识别 \blank{OCR}
    \end{question}
    \begin{question}
	保真度 \blank{fidelity}
    \end{question}
\end{fillin}

\begin{fillin}[title={Symbols and Formulas.(12 pts.)}, examcolumns=2, keycolumns=2]
\noindent{\bf Directions: }{\em Give the How-to-Read of the following
symbols and formulas.}
    \begin{question}
	$\epsilon$ \blank{epsilon}
    \end{question}
    \begin{question}
	$\zeta$ \blank{zeta}
    \end{question}
    \begin{question}
	$\Delta$ \blank{delta}
    \end{question}
    \begin{question}
	$3{2\over 3}$ \blank{three and two-third}
    \end{question}
    \begin{question}
	$b \propto c$ \blank{b is proportional to c}
    \end{question}
    \begin{question}
	$\sqrt[4]{c'}$ \blank{the fourth square root of c prime}
    \end{question}
\end{fillin}

\begin{shortanswer}[title={English-Chinese Translation. (20 pts.)}]
\noindent{\bf Directions: }{\em Read the following paragraph and translate the underlined sentences
into Chinese.}\bigskip

\begin{linenumbers*}
{\em Graphics} are internally represented as an assemblage of objects
such as lines, curves, or circles. We say that the representation is
aware of the {\em semantic} contents. They are {\em revisable}; that is,
objects can be individually deleted, added, moved, or modified later. In
contrast, {\em images} are not {\em revisable} in the sense given above.
They ignore the semantic contents. They are described as spatial arrays
of values. The smallest addressable image element is called a {\em
pixel}. The array, and thus the set of pixels, is called a {\em bitmap}.
\ul{$^{\ref{e2c1}}$Object-based editing is not possible---though autotracing tools which
can compute the bounds of bitmap areas may help---but image editing tools
exist for enhancing and retouching bitmap images.} \ul{$^{\ref{e2c2}}$The drawback of
bitmaps is that they need much more storage capacity than graphics, up
to two or three orders of magnitude.} \ul{$^{\ref{e2c3}}$Their advantage is that no
processing is necessary before displaying them, unlike with graphics
where the abstract definition must be processed first to produce a
bitmap.} \ul{$^{\ref{e2c4}}$Of course, images captured from an analog signal, via scanners
or video cameras, are represented as bitmaps, unless semantic
recognition takes place such as in }\underline{\em optical character recognition.}

\end{linenumbers*}

\begin{flushright}
--From {\em Multimedia Information and Systems}
\end{flushright}
    \begin{question}\label{e2c1}
    \ding{45}\examvspace*{1cm}
	\begin{answer}
	{\em (参考译文)}基于对象的编辑是不可能的~(虽然可以计算位图区域边
	界的描图工具或许会有帮助)~但是有编辑工具可以对位图进行加强和润饰
	。
	\end{answer}
    \end{question}
    \begin{question}\label{e2c2}
    \ding{45}\examvspace*{1cm}
	\begin{answer}
	{\em (参考译文)}位图的缺点就是比图形需要多得多的存储容量，能到
	~(图形存储量的)~2~到~3~个数量级的大小。
	\end{answer}
    \end{question}
    \begin{question}\label{e2c3}
    \ding{45}\examvspace*{1cm}
	\begin{answer}
	{\em (参考译文)}他们的优点是在显示之前不需处理，不像图形那样里边
	的抽象定义必须先被处理来产生位图。
	\end{answer}
    \end{question}
    \begin{question}\label{e2c4}
    \ding{45}\examvspace*{1cm}
	\begin{answer}
	{\em (参考译文)}当然，通过扫描仪或视频摄录机捕获的图像是以位图表
	示的，除非~(对它)~进行了意义识别比如光学字符识别。
	\end{answer}
    \end{question}
\end{shortanswer}

\begin{shortanswer}[title={Chinese-English Translation. (14 pts.)}]
\noindent{\bf Directions: }{\em Read the following paragraphs and
translate them into English.}\bigskip

\begin{linenumbers*}

\noindent{\bf 例 8-14} 给定图~8-30~中的电路，使用节点分析法求解电压
~$V_{ab}$。

\noindent{\bf 解}
\begin{minipage}[t]{16cm}
\noindent 步骤~1：选一个方便的参考节点。

\noindent 步骤~2：将电压源转换为等效的电流源。等效电路图如图~8-31~所示。

\noindent 步骤~3~和~4：任意地标识各节点电压和支路电流。根据假定的电流方
向标定所有电阻两端的电压极性。

\noindent 步骤~5：现在~$V_1$~和~$V_2$~两节点应用基尔霍夫电流定律：(略)。

\noindent 步骤~6：应用电阻两端的电压将电流重写如下：(略)，节点方程变为
~(略)，将电压表达式代入到原先的节点方程中，得到如下联立线性方程组：(略)
，进一步简化为~(略)。

\noindent 步骤~7：使用行列式求解节点电压得~(略)。
\end{minipage}

\end{linenumbers*}

\begin{flushright}
--From {\em Chapter 8, Circuit Analysis: Theory \& Practice} by Robbins, Allan
\end{flushright}
{\bf Tips:}
    \begin{tabular}[t]{ll}
    基尔霍夫 & Kirchhoff \\
    联立的 & simultaneous \\
    行列式 & determinant 
    \end{tabular}
    \begin{question}
    \ding{45}
    \examvspace*{20cm}
	\begin{answer}
	{\bf EXAMPLE 8-14} Given the circuit of Figure 8-30, use nodal
	analysis to solve for the voltage $V_{ab}$.

	{\bf Solution}

	{\bf Step 1:} Select a convenient reference node.

	{\bf Step 2:} Convert the voltage sources into equivalent
	current sources. The equivalent circuit is shown in Figure 8-31.

	{\bf Steps 3 and 4:} Arbitrarily assign node voltages and branch
	currents. Indicate the voltage polarities across all resistors
	according to the assumed current directions.

	{\bf Step 5:} We now apply Kirchhoff s current law at the nodes
	labelled as $V_1$ and $V_2$:  ...

	{\bf Step 6:} The currents are rewritten in terms of the
	voltages across the resistors as follows: ...\\
	The nodal equations become\\
	Substituting the voltage expressions into the original nodal
	equations, we have the following simultaneous linear
	equations:\\
	These may be further simplified as
	
	{\bf Step 7:} Use determinants to solve for the nodal voltages
	as ...
	\end{answer}
    \end{question}
\end{shortanswer}

\begin{fillin}[title={Cloze.(13 pts.)}, examcolumns=2, keycolumns=2]
\noindent{\bf Directions: }{\em Read the following passage carefully and
then fill each blank with one suitable word or expression selected from
the list.}\\
\begin{tabular}{llll}
energy & oscillator & theory & coil \\
frequency & propagate & electromagnetic & gap \\
oscillation & light & spark & electromagnetic field \\
free space (自由空间) & & & \\
\end{tabular}

\begin{linenumbers*}

In 1864, James Maxwell (麦克斯韦，1831-1879), a Scottish physicist,
produced his theory of the \underline{\ref{fil1}\hspace{12pt}} which
predicted that \underline{\ref{fil2}\hspace{12pt}} waves can
\underline{\ref{fil3}\hspace{12pt}} in
\underline{\ref{fil4}\hspace{12pt}} at a velocity (速度) equal to that
of \underline{\ref{fil5}\hspace{12pt}} . Experimental confirmation of
this \underline{\ref{fil6}\hspace{12pt}} had to wait until 1887 when
Heinrich Hertz (赫兹，1857-1894) constructed the first high-frequency
\underline{\ref{fil7}\hspace{12pt}}. When a voltage was induced in an
induction coil connected across a spark gap, a discharge would occur
across the \underline{\ref{fil8}\hspace{12pt}} setting up a damped
sinusoidal (正弦的) high-frequency \underline{\ref{fil9}\hspace{12pt}}.
The \underline{\ref{fil10}\hspace{12pt}} of the oscillation could be
changed by varying the capacitance of the gap by connecting metal plates
to it. The detector that he used consisted of a second coil connected to
a much shorter \underline{\ref{fil11}\hspace{12pt}} gap. The observation
of sparks across the detector gap when the induction coil was excited
showed that the electromagnetic \underline{\ref{fil12}\hspace{12pt}} from
the first coil was reaching the second
\underline{\ref{fil13}\hspace{12pt}} through space.

\end{linenumbers*}

\begin{flushright}
From Chapter 1 of {\em Telecommunication Circuit Design (Second
Edition)}\\
by Patrick D. van der Puije
\end{flushright}
    \begin{question}\label{fil1}
	\blank{electromagnetic field}
    \end{question}
    \begin{question}\label{fil2}
	\blank{electromagnetic}
    \end{question}
    \begin{question}\label{fil3}
	\blank{propagate}
    \end{question}
    \begin{question}\label{fil4}
	\blank{free space}
    \end{question}
    \begin{question}\label{fil5}
	\blank{light}
    \end{question}
    \begin{question}\label{fil6}
	\blank{theory}
    \end{question}
    \begin{question}\label{fil7}
	\blank{oscillator}
    \end{question}
    \begin{question}\label{fil8}
	\blank{gap}
    \end{question}
    \begin{question}\label{fil9}
	\blank{oscillation}
    \end{question}
    \begin{question}\label{fil10}
	\blank{frequency}
    \end{question}
    \begin{question}\label{fil11}
	\blank{spark}
    \end{question}
    \begin{question}\label{fil12}
	\blank{energy}
    \end{question}
    \begin{question}\label{fil13}
	\blank{coil}
    \end{question}
\end{fillin}

\begin{fillin}[title={Reading Comprehension.(14 pts.)}, examcolumns=2, keycolumns=2]
\noindent{\bf Directions: }{\em Read the following passage and fill in
the blanks of question \ref{lgk1} to \ref{lgk19} with the information in
the text.}\bigskip

\begin{linenumbers*}

\standardtilde
\centerline{\Large\bf What Is a Computer?}\bigskip

The basic job of computers is the \ul{processing} of information. For
this reason, computers can be defined as very-high-speed electronic
device which accept information in the form of instructions called a
program and characters called data, perform mathematical and/or logical
opreations on the information, and then supply results of these
operations. The program, or part of it, which tells the computers what
to do and the data, which provide the information needed to solve the
problem, are kept inside the computer in a place called \ul{memory}.

Computers are thought to have many remarkable powers. However, most
computers, whether large or small have three basic capabilities. First,
computers have circuits for performing arithmetic operations, such as:
addition, subtraction, multiplication, division and \ul{exponentiation}.
Second, computers have a means of communicating with the user. After
all, if we couldn't feed information in and get results back, these
machines wouldn't be of much use. However, certain computers (commonly
\ul{minicomputers} and \ul{microcomputers}) are used to control directly
things such as robots, aircraft navigation systems, medical instruments,
etc.

Some of the most common methods of inputting information are to use
magnetic tape, disks, and \ul{terminals}. The computer's input device
(which might be a keyboard, a \ul{tape drive} or disk drive, depending
on the medium used in inputting information) reads the information into
the computer. For outputting information, two common devices used are a
printer which prints the new information on paper, or a \ul{CRT} display
screen which shows the results on a TV-like screen.

Third, computers have circuits which can make decisions. The kinds of
decisions which computer circuits can make are not of the type: ``Who
would win a war between two countries?'' or ``Who is the richest person
in the world?'' Unfortunately, the computer can only decide three
things, namely: Is one number less than another? Are two numbers equal?
and, Is one number greater than another?

A computer can solve a series of problems and make hundreds, even
thousands, of logical decisions without becoming tired or bored. It can
find the solution to a problem in a fraction of the time it takes a
human being to do the job. A computer can replace people in dull,
routine tasks, but it has no originality; it works according to the
instructions given to it and cannot exercise any value judgements. There
are times when a computer seems to operate like a mechanical ``brain'',
but its achievements are limited by the minds of human beings. A
computer cannot do anything unless a person tells it what to do and
gives it the appropriate information; but because electric pulses can
move at the speed of light, a computer can carry out vast numbers of
arithmetic-logical operations almost instantaneously. A person can do
everything a computer can do, but in many cases that person would be
dead long before the job was finished.
\bigskip

\noindent{\large\bf Types of Computer}
\bigskip

\noindent{\bf Mainframes}

Computers come in a wide variety of sizes and capabilities. The largest
and most powerful are often called {\em mainframes}. Mainframe computers
may fill an entire room. They are designed to work at very high speeds
with large data words. typically 64 \ul{bits} or greater, and they have
massive amounts of memory. Computers of this type are used for military
defense control, business data processing (an insurance company, for
example). and for creating computer graphics displays for science
fiction movies. Examples of this type of computer are the IBM 4381, the
Honeywell DPS 8, and the CRAY X-MP/48.
\bigskip

\noindent{\bf Minicomputers}

Scaled-down versions of mainframe computers are often called {\em
minicomputers}. The main unit of a minicomputer usually fits in a single
\ul{rack} or box. A minicomputer runs more slowly, works directly with
smaller data words (often 32-bit words), and does not have as much
memory as a mainframe. Computers of this type are used for business data
processing, industrial control (an oil refinery, for example), and
scientific research. Examples of this type of computer are the Digital
Equipment Corp. VAX 11/730 and the Data General MV/8000 II.
\bigskip

\noindent{\bf Microcomputers}

As the name implies, {\em microcomputers} are small computers. They
range from small controllers that work directly with 4-bit words and can
\ul{address} a few thousand bytes of memory to large units that work
directly with 32-bit words and can address millions or billions of bytes
of memory. Some of the more powerful microcomputers have all or most of
the features of earlier minicomputers. Therefore, it has become very
hard to draw a sharp line between these two types. One distinguishing
feature of a microcomputer is that the CPU is usually a single
\ul{integrated circuit} called a \ul{microprocessor}. Older books often
used the terms microprocessor and microcomputer interchangeably, but
actually the microprocessor is the \ul{CPU} to which you add \ul{ROM},
\ul{RAM}, and ports to make a microcomputer. Microcomputers are used in
everything from smart sewing machines to computer-aided design systems.
Examples of microcomputers are the Intel 8051 single-chip controller;
the SDK-86, a single-board computer design kit; the IBM Personal
Computer (PC); and the Apple Macintosh computer.
\bigskip

\noindent{\large\bf Personal Computer}

Combining the words personal and computer may give you the impression
that personal computers are less \ul{sophisticated} than their larger
mainframe and minicomputer relatives. This is a \ul{misconception}.
Advances in technology have almost eliminated the gap that was formerly
inherent in size. Personal computer systems are highly evolved
descendants of earlier and larger computer systems.

Because of this evolution, most organizations are on the \ul{threshold}
of a new style of computing in which increasing amounts of computer
resources are allocated to individual users in the form of personal
computer systems. This new style of computing relies on the
communication concepts to link groups of computers of different sizes
and types so that components of a personal computer system.

The basic hardware components of a personal computer system consist of
\begin{shortitemize}
    \item Keyboard
    \item Display
    \item System unit
    \item Disk drives
    \item Printer
\end{shortitemize}

These components perform similar functions in computers of all types and
sizes. Familiarizing yourself with what they are and what they do will
help you make the connection between computer concepts and \ul{tangible}
hardware components.

Personal computer software comes in many different varieties, and the
applications number in the thousands, so it is useful to know how
individual programs are categorized. The broadest classifications of
software are system software and application software.

System software includes
\begin{shortitemize}
    \item Operating systems
    \item Programming languages
\end{shortitemize}

Application software includes
\begin{shortitemize}
    \item Special-purpose prgrams
    \item General-purpose prgrams
\end{shortitemize}

Using a personal computer involves getting used to the conventions of
the user interface and the operating system, and then developing an
understanding of what a computer can do by becoming familiar with some
of the application software for personal computers.

\end{linenumbers*}

\begin{flushright}
(1300 words)\\
From {\em Practical Microprocessor Interfacing} by S.~A.~Money
\end{flushright}

{\bf Tips:}\CJKtilde

    \begin{center}
    \tablefirsthead{}
    \tablehead{}
    \tabletail{}
    \tablelasttail{}
    \begin{supertabular}{p{6cm}lp{5cm}}
    process & {\em v.} & 处理 \\
    memory & {\em n.} & 存储器 \\
    exponentiation & {\em n.} & 取幂 \\
    minicomputer & {\em n.} & 小型计算机 \\
    microcomputer & {\em n.} & 微型计算机 \\
    terminal & {\em n.} & 终端 \\
    tape drive & & 磁带机 \\
    CRT (Cathode Ray Tube) & & 阴极射线管 \\
    mainframe & {\em n.} & 大型计算机 \\
    bit & {\em n.} & 位 \\
    rack & {\em n.} & 机柜 \\
    address & {\em v.} & 寻址 \\
    integrated circuit & & 集成电路 \\
    microprocessor & {\em n.} & 微处理器 \\
    CPU (Central Processing Unit) & & 中央处理器 \\
    ROM (Read Only Memory) & & 只读存储器 \\
    RAM (Random Access Memory) & & 随机存取存储器 \\
    sophisticated & {\em adj.} & 复杂的 \\
    misconception & {\em n.} & 误解 \\
    threshold & {\em n.} & 开始 \\
    tangible &{\em adj.} & 有形的
    \end{supertabular}
    \end{center}

\noindent{\bf Complete the following diagram and table with the
information in the text.}

\begin{center}
\setlength{\unitlength}{4144sp}%
\begin{picture}(4114,1644)(329,-983)
\thinlines
{\color[rgb]{0,0,0}\put(1016,449){\framebox(2570,200){A Personal
Computer System}}
}%
{\color[rgb]{0,0,0}\put(651,-16){\framebox(970,180){Sofware}}
}%
{\color[rgb]{0,0,0}\put(481,-506){\framebox(410,190){\ref{lgk1}}}
}%
{\color[rgb]{0,0,0}\put(1341,-496){\framebox(395,170){\ref{lgk2}}}
}%
{\color[rgb]{0,0,0}\put(341,-966){\framebox(320,170){\ref{lgk3}}}
}%
{\color[rgb]{0,0,0}\put(741,-966){\framebox(325,170){\ref{lgk4}}}
}%
{\color[rgb]{0,0,0}\put(1186,-971){\framebox(320,175){\ref{lgk5}}}
}%
{\color[rgb]{0,0,0}\put(1621,-971){\framebox(325,170){\ref{lgk6}}}
}%
{\color[rgb]{0,0,0}\put(2946,-16){\framebox(985,175){Hardware}}
}%
{\color[rgb]{0,0,0}\put(2391,-501){\framebox(325,180){\ref{lgk7}}}
}%
{\color[rgb]{0,0,0}\put(2806,-506){\framebox(325,180){\ref{lgk8}}}
}%
{\color[rgb]{0,0,0}\put(3211,-501){\framebox(320,170){\ref{lgk9}}}
}%
{\color[rgb]{0,0,0}\put(3626,-506){\framebox(325,180){\ref{lgk10}}}
}%
{\color[rgb]{0,0,0}\put(4116,-506){\framebox(315,175){\ref{lgk11}}}
}%
{\color[rgb]{0,0,0}\put(1091,164){\line( 0, 1){110}}
\put(1086,274){\line( 1, 0){2290}}
\put(3376,274){\line( 0,-1){115}}
}%
{\color[rgb]{0,0,0}\put(2261,444){\line( 0,-1){170}}
}%
{\color[rgb]{0,0,0}\put(711,-311){\line( 0, 1){145}}
\put(716,-166){\line( 1, 0){850}}
\put(1566,-166){\line( 0,-1){150}}
}%
{\color[rgb]{0,0,0}\put(1091,-26){\line( 0,-1){140}}
}%
{\color[rgb]{0,0,0}\put(511,-791){\line( 0, 1){185}}
\put(511,-606){\line( 1, 0){390}}
\put(901,-606){\line( 0,-1){185}}
}%
{\color[rgb]{0,0,0}\put(711,-511){\line( 0,-1){ 95}}
}%
{\color[rgb]{0,0,0}\put(1361,-801){\line( 0, 1){195}}
\put(1361,-606){\line( 1, 0){395}}
\put(1756,-606){\line( 0,-1){190}}
}%
{\color[rgb]{0,0,0}\put(2586,-331){\line( 0, 1){165}}
\put(2586,-166){\line( 1, 0){1695}}
\put(4281,-166){\line( 0,-1){155}}
}%
{\color[rgb]{0,0,0}\put(2976,-176){\line( 0,-1){140}}
}%
{\color[rgb]{0,0,0}\put(3796,-181){\line( 0,-1){145}}
}%
{\color[rgb]{0,0,0}\put(3376,-21){\line( 0,-1){305}}
}%
{\color[rgb]{0,0,0}\put(1576,-511){\line( 0,-1){ 95}}
}%
\end{picture}%
\bigskip

\begin{tabular}{|rccc|}\hline
Type & Size & Application & Example \\\hline
Mainframe & \ref{lgk12} & \ref{lgk14} & \ref{lgk17} \\\hline
Minicomputer & \ref{lgk13} & \ref{lgk15} & \ref{lgk18} \\\hline
Microcomputer & Desktop & \ref{lgk16} & \ref{lgk19}\\\hline
\end{tabular}
\end{center}

    \begin{question}\label{lgk1}
	\blank{System software}
    \end{question}
    \begin{question}\label{lgk2}
	\blank{Application software}
    \end{question}
    \begin{question}\label{lgk3}
	\blank{Operating systems}
    \end{question}
    \begin{question}\label{lgk4}
	\blank{Programming languages}
    \end{question}
    \begin{question}\label{lgk5}
	\blank{Special-purpose programs}
    \end{question}
    \begin{question}\label{lgk6}
	\blank{General-purpose programs}
    \end{question}
    \begin{question}\label{lgk7}
	\blank{Keyboard}
    \end{question}
    \begin{question}\label{lgk8}
	\blank{Display}
    \end{question}
    \begin{question}\label{lgk9}
	\blank{System unit}
    \end{question}
    \begin{question}\label{lgk10}
	\blank{Disk drives}
    \end{question}
    \begin{question}\label{lgk11}
	\blank{Printer}
    \end{question}
    \begin{question}\label{lgk12}
	\blank{Room-sized}
    \end{question}
    \begin{question}\label{lgk13}
	\blank{Rack-sized or box-sized}
    \end{question}
    \begin{question}\label{lgk14}
	\blank{Military defense control, business data processing, and
	creating computer graphics displays for science fiction movies}
    \end{question}
    \begin{question}\label{lgk15}
	\blank{Business data processing, industrial control, and
	scientific research}
    \end{question}
    \begin{question}\label{lgk16}
	\blank{Wide range of tasks, from smart sewing machines to
	computer aided design system}
    \end{question}
    \begin{question}\label{lgk17}
	\blank{IBM 4381; Honeywell DPS 8; CRAY XMP/48}
    \end{question}
    \begin{question}\label{lgk18}
	\blank{DEC VAX 11/730 and Data General MV/8000 II}
    \end{question}
    \begin{question}\label{lgk19}
	\blank{Intel 8051, SDK-86, IBM PC and Apple Macintosh}
    \end{question}
\end{fillin}

\begin{shortanswer}[title={\bf Writting. (12 pts.)}]
\noindent{\bf Directions: }{\em Write an abstract for the passage ``What
Is a Computer?'' of last section. The abstract should be limited to
50-200 words and should contain the most critical information of the
passage.}\bigskip
    \begin{question}
    \ding{45}
    \examvspace*{6cm}
	\begin{answer}
	(评分标准)语言部分参考四六级作文评分标准。Abstract 简要要求如下
	：\\
	The abstract should be limited to 50-200 words and should
	concisely state what was done, how it was done, principal
	results, and their significance. And should contain the most
	critical information of the paper.\\
	其它各项要求参考一般的摘要写作要求，规范与语言要求并重。
	\end{answer}
    \end{question}
\end{shortanswer}
\end{document}
\end{CJK*}
